---
title: "ReadMe"
author: "Andria Theron"
date: "September 29, 2017"
output: html_document
---


For gitignore:

.Rproj.user
.Rhistory
.RData
.RUserdata
Data/

NB Mathpix

Sumatra

#Aim

The aim of this paper is to simulate recommendations made on television programs by stock brokers. I am not enirely sure how to approach this project, but I think I am going to try to construct a portfolio that is equally weighted. My concern is that I will need to buy stocks everyday and work out the returns with regards to the present day.

#Techniques used

Practical 5

#Data

#Packages used

#Miscellaneous notes

***

#Paper

Every piece of code that you use in your paper must be here first

Do this super detailed

#Introduction

Programs for portfolios:
1. BusinessDayTV, Stock Watch Picks (South Africa)
2. CNBC, Fast Money (USA)
3. 

I chose these programs, because they include stock recommendations made by a public forum

#Methodology

List code

```{r}
list.files("Code", full.names = TRUE)
source(Code)
```

```{r initialize}

```

```{r Data Import}

```

```{r Returns create}



```

```{r}

```






#Literature review

#Results

#Conclusion